The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-17 paper/sections/methods.tex
added very rough draft for the raycasting quadrature section

\section{Selecting Centers of Mass}
\myworries{TODO. waiting to implement this before I start writing how we do it}
\section{Raycasting Quadrature}
\section{Dynamic Simulation}
\subsection{Generalized Inertia}
\subsection{Generalized Forces}
\subsection{Equations of Motion}
%This is most notable in cases where the degree of the polynomial on a NURBS is higher than the degree of the B-spline surface.

>>>>

\section{Selecting Centers of Mass}
\myworries{TODO. waiting to implement this before I start writing how we do it}
\section{Raycasting Quadrature}
The last step before we may discuss the dynamic simulation is to describe our strategy for generating material points $\mathbf{X}$ in the undeformed model. Our volume integration strategy is based on \cite{KHOSRAVIFARD201030} which we briefly describe in the following section
\subsection{Review of the Meshless Method for Domain Integral Evaluation in \cite{KHOSRAVIFARD201030}}
This paper addresses the integration of volume integrals of the form $\mathbf{I} = \int_\Omega f(\mathbf{x}) d\Omega$ where $\mathbf{x} = (x_1,x_2,x_3)$. The authors show that through application of the Green-Gauss theorem, this integral may be rewritten as 2D integral over a $yz$ plane where at each position along the plane we evaluate a line integral along the $x$-axis. To evaluate these line integrals, a raycasting procedure is performed to find a set of intersection along the line. These intersection define integration domains in which we sample 3D integration points. As a result of integrating over the 2D plane and raycasting at each 2D point, we produce an integration rule over the entire domain that can converge to the true integral value.

In our approach we modify the raycasting procedure by allowing integration over intersecting NURBS surfaces. It is common in NURBS modeling to produce models in which many surfaces overlap. To account for this we augment the raycasting intersection step to use an approach common in Constructive Solid Geometry (CSG). For the set of intersection intervals, we instead take the union over all intervals to yield a new set of intervals handling intersecting solids. We find that this extension serves as a simple and practical approach to support inexact models (\myworries{not sure what to right here}). We note that this solution is not perfect and making this intersection step more robust serves as future work.

\section{Dynamic Simulation}
\subsection{Generalized Inertia}
\subsection{Generalized Forces}
\subsection{Equations of Motion}
%This is most notable in cases where the degree of the polynomial on a NURBS is higher than the degree of the B-spline surface.
